Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-16 scripts/02_differential_expression_analysis.Rmd
adding a volcano plot

# Differential expression analysis
timecourse_contrasts = c("C-K", "C-M")

@@

pvalues = de_analysis
outname = ".results/pvalues.txt"
write.table(pvalues, outname, sep="\t")
```

>>>>

# Differential expression analysis
timecourse_contrasts = c("C-K", "C-M", "C-VL", "C-VH")

@@

pvalues = de_analysis
```

Let's explore a bit the number of genes found differentially expressed.

```{r}
print(colSums(pvalues[, grepl("-qval", colnames(pvalues))] < 0.05))
```

And now a volcano plot for quick visualization

```{r fig.height=8, fig.width=8}

pvalue = de_analysis[, "C-K-qval"]
lfc_epicon = de_analysis[, "C-K-lfc_epicon"]

plot(lfc_epicon, -log10(pvalue), pch=20, main="Volcano plot",
     xlim=c(-2.5, 2))

# Add colored points: red if padj<0.05, orange of log2FC>1, green if both)
points(lfc_epicon[pvalue < 0.01], -log10(pvalue[pvalue < 0.01]), pch=20,
       col="red")
points(lfc_epicon[abs(lfc_epicon) > 1],
       -log10(pvalue[abs(lfc_epicon) > 1]), pch=20, col="orange")
points(lfc_epicon[(pvalue < 0.01) & (abs(lfc_epicon) > 1)],
       -log10(pvalue[(pvalue < 0.01) & (abs(lfc_epicon) > 1)]), pch=20, col="green")

```

```{r echo=FALSE, results="hide"}
outname = ".results/pvalues.txt"
write.table(pvalues, outname, sep="\t")
```
